---
title: "R programming project 1"
author: "Doug Jacobson"
date: "Monday, October 20, 2014"
output: html_document
---

This program will read in pollution monitoring data for fine particulate matter (PM) at 332 locations within the USA.  Each file contains data for a single monitor.  

This function performs the following:
-Reads in a specified range of data sets ( 1:10 is data sets 1 through 10) from the working directory. 
-Will return the mean value of the selected pollutant; "sulfate", or "nitrates" may be used.  Empty values shall be excluded.

```{r}
#setwd(paste(getwd(),directory, sep="/"))
setwd("C:/Users/gongshow/Documents/R Projects/Coursera Projects/R Programming/specdata")
pollutantmean=function(pollutant, id = 1:332){
        
        
        lp= data.frame()
        files_list<- list.files(, full.names=TRUE, pattern="*.csv")
        listcsv = dir(pattern = "*.csv")  
        
        for(i in id){
          lp= rbind(lp, read.csv(listcsv[i], header=TRUE))  
        }
        
        if(pollutant == "sulfate"){
           sulfmean=mean(lp[ ,2], na.rm=TRUE)
           return(sulfmean)
         }
        
        if(pollutant == "nitrate"){
           nitratemean=mean(lp[ ,3], na.rm=TRUE)
           return(nitratemean)
         }
}
```


This function reports the number of observed cases in each data file.  It will return a vector with the number of observed cases along with the identifier (ID) of the data being taken.

```{r}
complete = function(id= 1:332){
          #setwd(paste(getwd(),directory, sep="/"))
        setwd("C:/Users/gongshow/Documents/R Projects/Coursera Projects/R Programming/specdata")
        nobs=data.frame()
        x=list()
        idNum=list()
        listcsv = dir(pattern = "*.csv")  
        for(i in seq_along(id)){
          lp= data.frame()
          lp= read.csv(listcsv[id[i]], header=TRUE)     
          x[i]=sum(!is.na(lp[, "sulfate"] &lp[ , "nitrate"] ))        
          idNum[i]=lp[ ,4]
          rm(lp)          
          }
          lst=rbind(idNum, x)
          nobs=data.frame(t(lst))
          return(nobs)
        }
```

This function looks at each ID station and will only return a correlation between nitrates and sulfates if a threshold of data samples is taken.  For example, a correlation is taken only if 100 samples have been measured at the site ID.  This function will look at all data files with the .csv extension in the working directory.  

```{r}
corr=function(threshold){
        
        setwd("C:/Users/gongshow/Documents/R Projects/Coursera Projects/R Programming/specdata")       
        lp=data.frame()
        threshCheck=vector()
        cr=vector()
        listcsv = dir(pattern = "*.csv") 
        k=1
        for(i in 1:332){
        threshCheck[i]= complete(i)[ , 2]
                if(threshCheck[i] > threshold) {
                        lp= na.omit(read.csv(listcsv[i], header=TRUE))
                        cr[k]=cor(lp[ ,2], lp[ ,3])
                        k=k+1
                      
                }
                                
        }
      return(cr)       
}




```
